Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2018-12-09 manuscript.Rmd
first draft

Selective attention is commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects [@logan_when_1979; @lowe_selective_1982; @west_effects_1998]. This result is usually  explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands [@logan_attention_1980; @logan_strategies_1984; @logan_when_1979; @lowe_selective_1982]. Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues [@brosowsky_memory-guided_2018; @bugg_support_2012; @egner_creatures_2014; @fischer_predicting_2015; @king_priming_2012; @mayr_outsourcing_2007].

>>>>

Selective attention is commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects [@logan_when_1979; @lowe_selective_1982; @west_effects_1998]. This result is usually  explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands [@logan_attention_1980; @logan_strategies_1984; @logan_when_1979; @lowe_selective_1982]. Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues [@brosowsky_memory-guided_2018; @bugg_support_2012; @egner_creatures_2014; @fischer_predicting_2015; @king_priming_2012; @mayr_outsourcing_2007].

### 2018-12-09 manuscript.tex
first draft

Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).

>>>>

Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).
